\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}


% Set your name here
\def\name{Adham Beykikhoshk}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Machine Learning, Bayesian nonparametrics, Data Mining},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}


% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}

% Place name at left
{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip


\begin{minipage}[t]{0.745\textwidth}
  Centre for Pattern Recognition and Data Analytics (PRaDA) \\
  Deakin University \\
  Geelong, VIC 3216 \\
  Australia
\end{minipage}
\begin{minipage}[t]{0.245\textwidth}
\begin{flushright}
  office: +61 3 5227 2150 \\
  mobile: +61 470 756 284  \\
  \href{mailto:abeyki@deakin.edu.au}{abeyki@deakin.edu.au} \\
  \href{https://adham.github.io/}{https://adham.github.io}
 \end{flushright}
\end{minipage}


\bigskip
\bigskip


\begin{minipage}[t]{0.195\textwidth}
Education
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}

\begin{itemize}
\item 2013 -- present {\bf PhD} in Computer Science, Deakin University, Australia \\
Thesis: Knowledge Discovery and Probabilistic modelling of Onlnie Autism Spectrum Disorder Data \\
Supervisors: Dr Dinh Phung, Dr Svetha Venkatesh, and Dr Ognjen Arandelovi{\'c}

\item 2011 -- 2012 {\bf MSc} with distinction in Artificial Intelligence,  
University of Southampton, United Kingdom \\
Thesis: Viewpoint Invariant Gait Energy Detection Image using Microsoft Kinect 
Supervisors: Dr. Mahesan Niranjan, Dr. Mark S. Nixon, and Dr John N. Carter

\item 2002 -- 2007 {\bf BSc} in Electrical Engineering, KNToosi University of Technology, Iran \\
Thesis: THESIS
Supervisors: Dr. Ali Khaki Sedigh, Dr Houman Sadjadian
\end{itemize}

\end{minipage}


\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Research \\
Interests
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{itemize}
\item Statistical Machine Learning, Bayesian Statistics, Data Mining
\end{itemize}
\end{minipage}

\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Publications 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{enumerate}

% you can add links to publications 
\item Beykikhoshk, A., Phung, D., Arandelovi{\'c}, O., and Venkatesh, S. (2016). Analysing 
the History of Autism Spectrum Disorder using Topic Models. To appear in the proceedings 
of \textit{IEEE International Conference on Data Science and Advanced Analytics (DSAA)}. IEEE.

\item Beykikhoshk, A., Phung, D., Arandelovi{\'c}, O., and Venkatesh, S. (2016). Discovering 
Topic Structure of a Temporally Evolving Document Corpus. To appear in Knowledge and Information 
Systems Journal. December 2015, \textit{arXiv preprint arXiv:1512.08008}

\item Beykikhoshk, A., Arandelovi{\'c}, O., Phung, D., and Venkatesh, S. (2015). Overcoming Data 
Scarcity of Twitter: Using Tweets as Bootstrap with Application to Autism-Related Topic Content Analysis. 
In the proceedings of \textit{IEEE/ACM International Conference on Advances in Social Networks Analysis 
and Mining (ASONAM)}, pp. 1354-1361, IEEE. doi:10.1145/2808797.2808908. 

\item Beykikhoshk, A., Arandelovi{\'c}, O., Phung, D., Venkatesh, S., and Caelli, T. (2015). Using Twitter 
to Learn About the Autism Community.  In \textit{Social Network Analysis and Mining}, 5(1), pp. 5-22. doi:10.1145/2808797.2808908

\item Beykikhoshk, A., Arandelovi{\'c}, O., Phung, D., and Venkatesh, S. (2015). Hierarchical Dirichlet 
Process for Tracking Complex Topical Structure Evolution and its Application to Autism Research Literature 
In the proceedings of \textit{Pacific Asia Conference on Knowledge Discovery and Data Mining (PAKDD)}, 
pp. 550-562. Springer International Publishing. doi:10.1007/978-3-319-18038-0\_43 

\item Beykikhoshk, A., Arandelovi{\'c}, O., Phung, D., Venkatesh, S., and Caelli, T. (2014). Data-mining 
Twitter and the Autism Spectrum Disorder: A Pilot Study In the proceedings of \textit{IEEE/ACM International 
Conference on Advances in Social Networks Analysis and Mining (ASONAM)}, pp. 349-356. IEEE.  doi:10.1109/ASONAM.2014.6921609 
\end{enumerate}
\end{minipage}


\begin{minipage}[t]{0.195\textwidth}
Publications 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{enumerate}
\setcounter{enumi}{6}

\item Ghofrani, Z., Mokhtarzade, M., Sahebi M.R., and Beykikhoshk, A. (2014) Evaluating Coverage Changes in National 
Parks using a Hybrid Change Detection Algorithm and Remote Sensing. In \textit{Journal of Applied Remote Sensing}, 8(1), pp. 083646-083646. doi:10.1117/1.JRS.8.083646. 
\end{enumerate}
\end{minipage}

\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Teaching 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{itemize}
\item An Introduction to Data Science, SIT112, Winter 2015, Deakin University \\
(It was the first time the course was being offered in Deakin University. The material I prepared, is still being used.)
\item An Introduction to Git, Winter 2016, Deakin Universoty, PRaDA
\end{itemize}
\end{minipage}


\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Employment 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{itemize}

\item March 2009 - September 2011, Fakoor Meghnatis Spadana, IT Manager \\
No. 14, 20th Street, Qaem Maqam Street, Tehran, Iran

\item Ferbruary 2010 - September 2011, Parsa International, IT Consultant \\
No. 5, Shabtab Street, North Qeytariyeh, Tehran, Iran

\item September 2010 - September 2011, Sadad Machine, IT Consultant \\
No. 12, North Razan Street, Mirdamad 13 Boulevard, Tehran, Iran

\item January 2007 - November 2008, Karino, IT Manager \\
No. 1488, Madani Street, Resalat Square, Tehran, Iran

\end{itemize}
\end{minipage}


\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Computer \\
Skills 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{itemize}
\item Programming: C, C++, Python, Julia, Matlab, R
\item Visualization: D3.js, JavaScript
\item Distributed computing: Apache Spark, Hadoop
\item Document preparation: \LaTeX, LyX
\end{itemize}
\end{minipage}

\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Software \\
Packages 
\end{minipage}
\begin{minipage}[t]{0.795\textwidth}
\begin{itemize}
\item BIAS.jl, \href{https://github.com/adham/BIAS.jl}{https://github.com/adham/BIAS.jl} \\
Bayesian Inference At Scale. It is a package written in Julia for Bayesian inference and modelling with large scale data. 
\item BNP.jl, \href{https://github.com/adham/BNP.jl}{https://github.com/adham/BNP.jl} \\
Bayesian Non-Parametrics. It is a package written in Julia for non-parametric Bayesian modelling.
\end{itemize}
\end{minipage}


\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
Awards and \\
Scholarships
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
\begin{itemize}
\item Full scholarship for PhD at Deakin University (Tuition fees + stippend) \\
NICTA
\item Tuition fees scholarship for MSc at University of Southampton \\
Aga Khan Foundation

\end{itemize}
\end{minipage}


\bigskip
\bigskip

\begin{minipage}[t]{0.195\textwidth}
References
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
\begin{itemize}
\item Upon request

\end{itemize}
\end{minipage}



%  \bigskip
% {\small Last updated: \today}

\end{document}

